\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity}

### 2013-09-25 docs/proposal/doc.tex
poging tot begin van gantt-chart

@@

\subsection*{Causal discovery methods}
The first causal method that we will use to find effective connectivity will be the PC-algorithm.
This is a state of the art used for general causal discovery, which finds the structure and the direction of connections of this network.
The structure of a network can also be given as input, for which the PC-algorithm can determine the directions.
Another causal discovery method is the BCCD-algorithm \cite{claassen2012}, which gives similar results as PC.
This algorithm has some useful properties; it is based on a Bayesian approach and as such, it is robust.
It also does not need any assumptions beforehand.
Because of this, the algorithm performs at least as good as other causal discovery algorithms such as FCI and PC in benchmarks on representative datasets, and in some cases it performs better.
BCCD also finds the reliability of found connections, giving additional information compared to PC and FCI.

@@

\section{Methods \& Strategy}
%Short general introduction to both methods
In this project, causal discovery algorithms will be applied to a dataset of functional and structural connectivity, in order to find effective connectivity.
For this, implementations of PC and BCCD can be used.
PC is a widely used algorithm and as such, many implementations already exist.
An implementation of BCCD suitable for this project also exists at the department of Intelligent Systems of the Radboud university.
The datasets of structural and functional connectivity are available, so the first step of this step will be to get the implementations for the algorithms working on the dataset.
This will result in a connectivity matrix which represents the effective connectivity.
These results will  be evaluated by cross-subject comparison, to see whether the gained data is consistent.
If it is, then this algorithm is a potentially useful algorithm for determining effective connectivity.
As PC is a state-of-the-art algorighm \cite{spirtes2000}, and BCCD shows a good potential \cite{claassen2012}, this way of determining effective connectivity may very well be the case.

@@

\section{Time schedule}

>>>>

\usepackage{pgfgantt}

@@

\subsection*{Causal discovery methods}
The first causal method that we will use to find effective connectivity will be the PC-algorithm.
This is a state of the art used for general causal discovery, which finds the structure and the direction of connections of this network.
If a graph skeleton of a network is already known beforehand, this can also be used as a basis such that the PC-algorithm can determine the directions.
Another causal discovery method is the BCCD-algorithm \cite{claassen2012}, which gives similar results as PC.
This algorithm has some useful properties; it is based on a Bayesian approach and as such, it is robust.
It also does not need any assumptions beforehand.
Because of this, the algorithm performs at least as good as other causal discovery algorithms such as FCI and PC in benchmarks on representative datasets, and in some cases it performs better.
BCCD also finds the reliability of found connections, giving additional information compared to PC and FCI.

@@

\section{Methods \& Strategy}
%Short general introduction to both methods
In this project, causal discovery algorithms will be applied to a dataset of functional and structural connectivity, in order to find effective connectivity.
For this, implementations of PC and BCCD can be used.
PC is a widely used algorithm and as such, many implementations already exist.
An implementation of BCCD suitable for this project also exists at the department of Intelligent Systems of the Radboud university.

The datasets of structural and functional connectivity are available, so the first step of this step will be to get the implementations for the algorithms working on the dataset.
We will first try the PC-algorithm, for which a suitable implementation still needs to be found. This will be done by using only functional connectivity data and also by providing strucural connectivity data as a graph skeleton.
The BCCD-algorithm will be used afterwards, which will also be used with only functional data as well as with functional and structural connectivity data.
This will result in a connectivity matrix which represents the effective connectivity.
These results will then be evaluated by cross-subject comparison, to see whether the gained data is consistent.
If it is, then this algorithm is a potentially useful algorithm for determining effective connectivity.
As PC is a state-of-the-art algorighm \cite{spirtes2000}, and BCCD shows a good potential \cite{claassen2012}, this way of determining effective connectivity may very well be the case.

@@

% week 50 is deadline voor draft, 51 is presentaties, 2 inleveren van final
\section{Time schedule}
\begin{ganttchart}{1}{10}
\gantttitle{2011}{10} \\
\gantttitlelist{40,...,52,1,2}{1} \\
\ganttgroup{Group 1}{1}{7} \\
\ganttbar{Task 1}{1}{2} \\
\ganttlinkedbar{Task 2}{3}{7} \ganttnewline
\ganttmilestone{Milestone}{7} \ganttnewline
\ganttbar{Final Task}{8}{12}
\ganttlink{elem2}{elem3}
\ganttlink{elem3}{elem4}
\end{ganttchart}
